Conjure: Summoning Proxies from Unused Address Space

### 2019-09-25 paper/paper.tex
5.1 pass

To achieve high-performance necessary to operate at 20~Gbps, we used
PF\_RING~\cite{pfring} to load balance incoming packets over 4~CPU cores. PF\_RING
supports balancing across cores based on flow (5-tuple) or source and
destination IPs. However, both of these options present engineering challenges
for \scheme that we must overcome.
One issue is that registrations could be processed on a
different core than the packets sent to that specific phantom host address. For
instance, a client could have its registration handled by Core 1, while its
packets to the phantom host address end up on Core 3, which doesn't know about the
original registration.

To address this, we used Redis~\cite{redis} to allow each process to broadcast
(publish) newly registered decoys to the other cores so they can
add them to their local list of registered phantom host addresses.
However, this introduces two new problems. First, a core might add a
registration \emph{after} it has already received and processed packets destined
for the specified phantom host. This typically isn't a problem when running on a
single core, as packets are processed sequentially. Second, each core may
timeout each phantom host at different times, potentially leading to differing
behavior that is visible to a censor. For instance, if we used the
source/destination IPs to load balance, a censor's packets to a phantom host could
be processed by a different core than the client. If the censor waits for the
known timeout before sending a probe, its core may have timed out that phantom host, while the client's core has refreshed the timeout of the phantom host due
to active use.

To address the first issue of asynchronous cores, we force the client to delay sending its connection
to the phantom host until a short time after registration. In practice, we force
the client to wait until the registration decoy responds before starting a
connection with the registered phantom host. While the decoy response is
unrelated to the station's processing, it serves as a conservative way to know
the registration has had time to reach the station.

To address the second issue of differing core timeouts, we implemented a new
load-balancing algorithm in
PF\_RING to select the core based solely on the destination IP address of the
packet. We still must use Redis to tell all of the cores of new
registrations, but only one core will be ultimately responsible for processing all of
the packets sent to a given phantom host, regardless of who sends it or when it is sent.

>>>>

To achieve performance needed to operate at 20~Gbps, we used
PF\_RING~\cite{pfring} to load balance incoming packets across 4~CPU cores,
which each run a dedicated detector process.
PF\_RING supports load balancing packets based on
either their flow (5-tuple), or their source/destination IPs, which allows
connections to be processed by a single process without
requiring communication across independent cores.

However, in \scheme, registration connections and phantom proxy connections
could end up being load balanced to different cores. In order for an individual
detector process to forward phantom proxy connections to the application, it must
know about the original registration, even if that registration was observed by a
different core.
To address this, we used Redis~\cite{redis} to allow each core's process to broadcast
(publish) newly registered decoys to the other cores so they can
add them to their local list of registered phantom host addresses. Broadcasting
registrations across all cores ensures that each detector process sees all
registrations, and can forward phantom proxy connections accordingly.

A second problem arises when considering how to \emph{timeout} unused phantom proxies
in the detector. When a phantom proxy is timed out, it no longer responds to any
active probes. A naive implementation might simply have each core timeout unused
phantom proxies after they go unused for a set time. However, this could leave
one core (that sees active proxy use) forwarding packets to the application, while
other cores (that do not see use) would timeout the proxy. A censor could probe the
phantom proxy and observe this behavior: if the censor's packets are processed
on a forwarding core, the censor can establish a TCP connection with the phantom
application. Otherwise, if they are processed on a timed out core, the censor's packets
will be ignored. Through multiple connections, the censor could use this strange
behavior (of intermittent TCP response) to identify and block potential phantom
proxies.

To address this issue of differing core timeouts, we implemented a new
load-balancing algorithm in
PF\_RING to select the core based only off the destination IP address of a
packet. This means that \emph{all} packets sent to a particular phantom proxy address
are processed by the same detector core, which allows the phantom proxy's timeout state
to be consistent regardless of what source attempts to connect to it.
%We still must use Redis to tell all of the cores of new
%registrations, but only one core will be ultimately responsible for processing all of
%the packets sent to a given phantom host, regardless of who sends it or when it is sent.
